### 2021-05-09 papers/SYRCoSE/regmachine-eventstruct.tex
regmachine-eventstruct.tex: commas and articles

The event structure is constructed incrementally 
in a step-by-step fashion by adding a single event 
on each step. In order to generate a new event 
on each step we require that events behave as \emph{identifiers}.

@@

We use the inverse covering function because it is 
more convenient in our setting. Indeed, the semantics adds a new event
at each step. Then it is convenient to require that in addition 
the small-step relation is provided with the $\lPO$ and $\lRF$
predecessors of a new event.

@@

We also need a way to reconcile the event structure
with the states of machine's threads. 
To do so we use a function ${\thrdmap : \eventSet \fun \ThrdState}$
which maps an event to a thread state obtained as the result of
the execution of the event's side-effect.

>>>>

The event structure is constructed incrementally 
in a step-by-step fashion by adding a single event 
on each step. In order to generate a new event 
on each step, we require that events behave as \emph{identifiers}.

@@

We use the inverse covering function because it is 
more convenient in our setting. Indeed, the semantics adds a new event
at each step. Then it is convenient to require that, in addition,
the small-step relation is provided with the $\lPO$ and $\lRF$
predecessors of a new event.

@@

We also need a way to reconcile the event structure
with the states of the machine's threads. 
To do so, we use a function ${\thrdmap : \eventSet \fun \ThrdState}$
which maps an event to a thread state obtained as the result of
the execution of the event's side-effect.
